InformatiCup 2024 Ctrl-Alt-Defeat

### 2024-01-14 paper.tex
Update paper.tex
Co-authored-by: RaphaW <116720366+RaphaW@users.noreply.github.com>

\subsubsection{Image generating models}

\textbf{Winston AI} is a commercial AI text detector that starts at 18\$ a month. They have two primary methods for checking if a text is AI written. Firstly linguistic analysis analyses every text for characteristics, that are different between human- and AI-generated work. One example characteristic is the repetitiveness, another is Data Training, where the detector saw many AI written texts of one model and learned unique characteristics that this model uses which then can be detected. So this method is more generator-specific. \cite{WinstonAI}

>>>>

\subsubsection{Image generating models}
The first image generative model we use is the Stable Diffusion model. It is developed by engineers and researchers from CompVis (\url{https://github.com/CompVis}), Stability AI (\url{https://stability.ai/}) and LAION (\url{https://laion.ai/}) \cite{patil2022stable}.

Diffusion models achieve state-of-the-art synthesis results on image data by decomposing the image formation process into sequential applications of denoising autoencoders. Due to its work directly in pixel space, they are very computational expensive. To lower the computational costs, the Stable Diffusion model is applied in a latent space of powerful pretrained autoencoders. This works without losing quality and flexibility. \cite{Rombach_2022_CVPR}
